<<<<<<< HEAD
---
output:
  md_document:
    variant: markdown_github
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# MME

MME is an R package providing a method to fit univariate and multivariate mixtures of Erlang distributions to possibly censored and/or truncated data. The censoring and/or truncation can be left, right or interval.

## Installation

To install the current development version from github you need the [devtools package](http://cran.r-project.org/web/packages/devtools/index.html) and the other packages on which MME depends:

```{r, eval = FALSE}
install.packages(c("devtools", "doParallel", "foreach", "matrixStats", "parallel"))
```

To install MME run:

```{r, eval = FALSE}
library(devtools)
install_github("RoelVerbelen/MME")
```

||||||| merged common ancestors
=======
---
output:
  md_document:
    variant: markdown_github
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# MME

MME is an R package providing a method to fit univariate and multivariate mixtures of Erlang distributions to possibly censored and/or truncated data. The censoring and/or truncation can be left, right or interval.

## Installation

To install the current development version from github you need the [devtools package](http://cran.r-project.org/web/packages/devtools/index.html) and the other packages on which MME depends:

```{r, eval = FALSE}
install.packages(c("doParallel", "foreach", "matrixStats", "parallel"))
```

To install MME run:

```{r, eval = FALSE}
# install.packages("devtools")
library(devtools)
install_github("RoelVerbelen/MME")
```

>>>>>>> 21c2c7567b42cacb3c6103c4f1a183752d694350
